        // variables
        "variables", "variable", "vars","var"

        / auto
        "auto","aut",  
        
        / constexpr 
        "constexpr",
        "constexp","constex", 
        "constex","conste",
        "contexp","contex","conte",
        
        / ternary operator
        "ternary operator","ternaryoperator", "ternary op",  
        "ternaryop", "tern operator","ternoperator", "ternary",  
        "tern op", "tern", "ternop",  
        /
        / scope
        "out of scope","outofscope","out scope" 
        "outscope", "in scope", "inscope",
        "scopes","scope","scop", 
        /
        / chaining
        "chaining", "chains","chain"
        /
        / streams 
        "streams","stream",
        "strea", 
        /
        / sstream 
        "sstrea","sstreams","s streams","s stream","sstream", 

        / touples
        "touples","touple","toup", "}, 
        
        / enums
        "enums","enum","enus","enu", , 

        / enum array mapping
        "enums arrays","enumsarrays",  
        "enums array","enumsarray","enum arrays",  
        "enumarrays","enum array",  
        "enumarray","enum ars",  
        "enum as","enum ar",  
        "enum a","enumar",  
        "enuma",  
        
        / enum vector mapping
        "enums vectors",  
        "enumsvectors",  
        "enums vector",  
        "enumsvector",  
        "enum vectors",  
        "enumvectors",  
        "enum vector",  
        "enumvector",  
        "enum vect",  
        "enumvect",  
        "enum vec",  
        "enumvec",  
        "enum v ",  
        "enumv",  
        /{"", 
        
        / arrays
        "arrays", "array", "arr","arra", 

        / dynamic arrays allocation
        "dynamic array allocation",  
        "dynamicarrayallocation",  
        "allocate dynamic array",  
        "allocatedynamicarray",  
        "dynamic arrays",  
        "dynamicarrays",  
        "dynamic array",  
        "dynamicarray",  
        "dyn arrays", "dynarrays","dyn array","dynarray", "darrays", "darray",  

        / vectors
        "vectors","vector",
        "vect","vec",

        / size_t 
        "size t","sizet","sizt","st"
        
        / conditional
        "conditionals", "conditional","conditions","condition", "if", "elseif", "else if","elsif","con","cond"

        / switch statements
        "switchstatement", 
        "switch statement", 
        "casestatement", 
        "case statement", 
        "case", 
        "switch", 

        / loops
        "iteration", ,
        "iterate", ,
        "iterator", 
        "iterators", 
        "iterating", 
        "loops", ,
        "loop", ,
        "lop", ,

        / ranges
        "ranges", }, 
        "range", }, 
        "ran", }, 
        
        / range pipes
        "ranges pipes", 
        "rangespipes",
        "ranges pipe",
        "rangespipe",
        "range pipe",
        "rangepipe",
        "rangep", 
        "ranp", 

        / range-based for loops
        "ranges loops",  
        "rangesloops",  
        "ranges loop",  
        "rangesloop",  
        "range loops",  
        "rangeloops",  
        "range loop",  
        "rangeloop",  
        "rloops",  
        "rloop",  

        / accidental conversions
        "conversions","conversion"
        /
        / accidental slicing 
        "slicing","sliced","slices", "slice",
        /
        / functions
        "functions","function", "func","fun",
        /
        / inline functions
        "inline functions",  
        "inlinefunctions",  
        "inlinefunction",  
        "inline fun",  
        "inlinefun",  
        "inlinef", 
        "inline", 
        "inli", 
        "inl", 
        / {"", 
        /
        / member functions
        "member function",  
        "memberfunction",  
        "memfunction",  
        "member",  
        "mem",  
        "member",  
        "memfun",  
        "class function",  
        "classfunction", 
        "classfunctions", 
        "classfunc",  
        "classfun",  
        /
        / public functions
        "public function", 
        "publicfunction", 
        "publicfun", 
        "pubfunc", 
        "pubfun", 
        "public",  
        "pub",  
        /
        / overloading functions
        "overloading functions", 
        "overload functions", 
        "overload function", 
        "function overload", 
        "functionoverload", 
        "functionoverloading", 
        "fun overload", 
        "fun overloading", 
        "funoverload", 
        "funoverloading", 
        "overfunction",  
        "overload",  
        "overloading", 
        "overloaded",  
        "overfun",  
        "over",  
        /
        / parameters
        "parameters",  
        "parameter",  
        "params",  
        "param",  
        "pars",  
        "par",  
        /
        / pass by value
        "pass by value", ue. 
        "passby value", ue. 
        "pass byvalue", ue. 
        "pass by val", ue. 
        "passbyvalue", ue. 
        "passvalue", ue. 
        "pass value", ue. 
        "passbyval", ue. 
        "byvalue", ue. 
        "byval", ue. 
        /
        / pass by reference
        "passing by reference",  
        "passing by ref",  
        "passingbyreference",  
        "passingreference",  
        "passbyreference",  
        "passreference",  
        "passbyref",  
        "passrefs",  
        "passref",  
        "byreference", 
        "byref", 

        / parameters default values 
        "default parameters",  
        "default parameter",  
        "defaultparameter",  
        "default params",  
        "defaultparams",  
        "default arguments",  
        "defaultarguments",  
        "default argument",  
        "defaultargument",  
        "default arg",  
        "defaultarg",  
        "default",  
        /
        / references 
        "references",  
        "reference",  
        "refer",  
        "ref",  
        /
        / dereference 
        "dereferencing", . 
        "unreference", . 
        "deref", . 
        "unref", . 
        /
        / references const 
        "const references"
        "constreferences",
        "const reference",
        "constreference", 
        "references const"
        "referencesconst",
        "reference const",
        "referenceconst", 
        "const refs"
        "constrefs",
        "const ref",
        "constref", 
        /
        / reference operator 
        "ref operator",
        "refoperator", 
        "refop",
        /
        / address operator 
        "address operator",  
        "addressoperator",  
        "addressop",  
        "address",  
        "add",  
        /
        / pointers
        "pointers",
        "pointer",
        "point",
        /
        / null pointer
        "null pointers"
        "nullpointers",
        "null pointer",
        "nullpointer", 
        "nullpoint",
        "point null",
        "pointnull", 
        /
        / nullptr
        "nullptr",
        "null ptr",
        "nulptr",
        "nullp",
        "null",
        /
        / unique pointer
        "unique pointers",
        "uniquepointers", 
        "unique pointer", 
        "uniquepointer"
        "uniquepoint", 
        "make unique", 
        "makeunique",
        "uniqueptr",
        "unique",
        /
        / pointer of pointer
        "pointer of pointer"
        "pointerofpointer", 
        "pointerpointer",
        "point to pointer", 
        "pointtopointer",
        "pointtopoint",
        "pointpoint",
        /
        / smart pointer
        "smart pointers"
        "smart pointer",
        "smartpointers",
        "smartpointer", 
        "smart ptr",
        "smartptr", 
        "smart",
        /
        / allocation 
        "allocations"
        "allocation",
        "allocating",
        "allocate",
        "allo"
        /
        / deallocation 
        "deallocating",
        "deallocations"
        "deallocation",
        "deallocated", 
        "deallocate", n
        "deal", n.cpp"}
        /
        / freeing memory 
        "freeing memory",  
        "freeingmemory",  
        "free memory",  
        "freememory",  
        "freeing", 
        "free", 
        / {"", 
        /
        / leaking memory 
        "leaking memory", 
        "leakingmemory", 
        "leaking", 
        "leaks", 
        "leak", 
        / {"", 
        /
        / classes 
        "classes", "}, 
        "class", "}, 
        "clas", "}, 
        "cla", "}, 
        /
        / class components 
        "classcomponents",  
        "class components",  
        "classcomponent",  
        "clascomponent",  
        "clacomponent",  
        "classcomp",  
        "components",  
        "component",  
        /
        / span 
        "spans",  
        "span",  
        "spa",  
        /
        / templates
        "templates", pp"}, 
        "template", pp"}, 
        "templat", pp"}, 
        "temps", pp"}, 
        "temp", pp"}, 
        /
        / template basics 
        "template basics",  
        "template basic",  
        "basic template",  
        "basictemplate",  
        "templatebasics",  
        "temp basics",  
        "temp basic",  
        "tempbasics",  
        "basicstemp",  
        "basictemp",  
        / {"", 
        /
        / variadic templates
        "variadic template",  
        "variadictemplates",  
        "variadictemplate",  
        "variatemplates",  
        "variatemplate",  
        "variadictemp",  
        "variatemp",  
        "variadic",  
        "varia",  
        / {"", 
        /
        / class template argument deduction 
        "classtemplates",  
        "classtemplate",  
        "classtemp",  
        "ctad", 
        /
        / templates auto return types 
        "auto templates",  
        "autotemplates",  
        "auto template",  
        "autotemplate",  
        "templates auto",  
        "template auto",  
        "templateauto",  
        "autotemp",  
        "tempauto",  
        /
        / return value optimization 
        /
        / structs 
        "structs", "}, 
        "struct", "}, 
        "s", "}, 
        /
        / structs against classes 
        "structs vs classes",  
        "structsvsclasses",  
        "structs and classes",  
        "structsandclasses",  
        "classes and structs",  
        "classesandstructs",  
        "structsandclasses",  
        "structsclasses",  
        "structs classes",  
        "structclasses",  
        "structvsclass",  
        "structclass",  
        "classesvsstructs",  
        "classesvsstruct",  
        "classstruct",  
        /
        / lambdas
        "lambdas"
        "lambda"
        "lambd"
        "lamb"
        "lam"
        /
        / lambdas captures
        "lambda captures",  
        "lambda capture",  
        "lambdacapture",  
        "lambdascaptures",  
        "lambdas captures",  
        "lambdas capture",  
        "lambdascapture",  
        "lambdascaptures",  
        "capturing",  
        "capture",  
        / {"", 
        /
        / lambdas captures by value
        "capture by value",  
        "capture by val",  
        "capturebyvalue",  
        "capturebyval",  
        "capturing by value",  
        "capturing by val",  
        "capturingbyvalue",  
        "capturingbyval",  
        "capturingval",  
        "capturevalue",  
        "captureval",  
        /
        / lambdas captures by reference 
        "capture by reference",  
        "capturebyreferences",  
        "capturebyreference",  
        "capturereferences",  
        "capturereference",  
        "capturerefs",  
        "captureref",  
        "capturing by reference",  
        "capturingbyreferences",  
        "capturingbyreference",  
        "capturingreferences",  
        "capturingreference",  
        "capturingrefs",  
        "capturingref",  
        /
        / lambdas captures by values and references 
        "capturing both",  
        "capturingboth",  
        "captures both",  
        "capturesboth",  
        "capture both",  
        "captureboth",  
        "both captures",  
        "bothcaptures",  
        "both capture",  
        "bothcapture",  
        /
        / lambda auto
        "lambdas auto",
        "lambda auto",
        "lambdasauto"
        "lambdaauto",
        "lamb auto",
        "lambauto",
        "auto lambdas",
        "auto lambda",
        "autolambdas",
        "autolambda",
        "autolamb",
        /
        / generic lambdas
        "generic lambdas",  
        "genericlambdas",  
        "generic lambda",  
        "genericlambda",  
        "genericlamb",  
        "gen lambdas",  
        "genlambdas",  
        "gen lambda",  
        "gen lamb",  
        "genlamb",  
        / {"", 
        /
        / variadic lambdas 
        "variadic lambdas", mbdas. 
        "variadiclambdas", mbdas. 
        "variadic lambda", mbdas. 
        "variadiclambda", mbdas. 
        "varia lambda", mbdas. 
        "varialambda", mbdas. 
        "varia lamb", mbdas. 
        "varialamb", mbdas. 
        "var lambdas", mbdas. 
        "varlambdas", mbdas. 
        "varlambda", mbdas. 
        "var lambda", mbdas. 
        "varlamb", mbdas. 
        "var lamb", mbdas. 
        / {"", mbdas.
        /
        / const lambdas 
        "const lambdas", as. 
        "constlambdas", as. 
        "const lambda", as. 
        "constlambda", as. 
        "const lamb", as. 
        "constlamb", as. 
        "lambdas const", as. 
        "lambdasconst", as. 
        "lambda const", as. 
        "lambdaconst", as. 
        "lamb const", as. 
        "lambconst", as. 
        / {"", as.
        /
        / concepts 
        "concepts", p"}, 
        "concept", p"}, 
        "conc", p"}, 
        / {"", p"},
        /
        / constants 
        "constants", pp"}, 
        "constant", pp"}, 
        "consts", pp"},
        "const", pp"},
        "cons", pp"},
        / {"", pp"}, 
        /
        / factories 
        "factories", pp"}, 
        "factory", pp"}, 
        "fact", pp"}, 
        "fac", pp"}, 
        / {"", pp"},
        /
        / virtual factories 
        "virtual factories", tories. 
        "virtualfactories", tories. 
        "virtual factory", tories. 
        "virtualfactory", tories. 
        "virtualfac", tories. 
        "virtfac", tories. 
        "virt", tories. 
        / {"", tories.
        /
        / constructors 
        "constructing", s. 
        "construction", s. 
        "constructed", s. 
        "constructors", s. 
        "constructor", s. 
        "construct", s. 
        / {"", s.
        /
        / destructors
        "destruction", . 
        "destructing", . 
        "destructors", . 
        "destructor", . 
        "destruct", . 
        "destroy", . 
        / {"", .
        /
        / automatic destructors 
        "automatic destructor", estructors. 
        "automaticdestructor", estructors. 
        "automatic destruction", estructors.
        "automaticdestruction", estructors.
        "auto destruction", estructors. 
        "autodestruction", estructors. 
        "auto destructor", estructors. 
        "autodestructor", estructors. 
        "auto destruct", estructors. 
        "autodestruct", estructors. 
        "auto destroy", estructors. 
        "autodestroy", estructors. 
        / {"", estructors.
        /
        / deterministic object lifetime and destruction
        "deterministic", ic_object_lifetime_and_destruction. 
        "determinism", ic_object_lifetime_and_destruction. 
        "deter", ic_object_lifetime_and_destruction. 
        / {"", ic_object_lifetime_and_destruction.
        /
        / RAII 
        /{"",  
        /{"", 
        /
        / new keyword 
        "new", . 
        / {"", .
        /
        / thread_local
        "thread local", l. 
        "threadlocal", l. 
        "local thread", l. 
        "localthread", l. 
        "thread", l. 
        / {"", l.
        /
        / static 
        "static objects", }, 
        "staticobjects", }, 
        "static object", }, 
        "staticobject", }, 
        "statics", }, 
        "static", }, 
        "stat", }, 
        / {"", },
        
        / dynamic 
        "dynamic objects", "}, 
        "dynamicobjects", "}, 
        "dynamic object", "}, 
        "dynamicobject", "}, 
        "dynam", "}, 
        "dyn", "}, 
        / {"", "},
        /
        / fmt format library
        "fmt format", library.
        "fmtformat", library.
        "fmt library", library.
        "fmtlibrary", library.
        "fmt lib", library.
        "fmtlib", library.
        "fmt", library.
        / {"", library. 
        /  
        / string_view
        "string view", . 
        "stringview", . 
        "view string", . 
        "viewstring", . 
        / {"", .
        /
        / structured bindings
        "structured bindings", bindings. 
        "structuredbindings", bindings. 
        "structured binding", bindings. 
        "structuredbinding", bindings. 
        "structure bindings", bindings. 
        "structurebindings", bindings. 
        "structure binding", bindings. 
        "structurebinding", bindings. 
        "struct bindings", bindings. 
        "structbindings", bindings. 
        "struct binding", bindings. 
        "structbinding", bindings. 
        "bindings", bindings. 
        "binding", bindings. 
        / {"", bindings. 
        /
        / arguments 
        "arguments", pp"},
        "argument", pp"},
        "args", pp"},
        "arg", pp"},
        / {"", pp"}, 
        /
        / flags 
        "options", ,
        "option", ,
        "flags", ,
        "flag", ,
        /
        / user input 
        "prompt user",  
        "promptuser",  
        "askuser",  
        "ask user",  
        "user response",  
        "userresponse",  
        "user answer",  
        "useranswer",  
        "prompting",  
        "prompt",  
        "answer",  
        "user",  
        / {"", 
        /
        / type 
        "types",  
        "type",  
        "typ",  
        "", 
        /
        / return type 
        "return types", . 
        "returntypes", . 
        "return type", . 
        "returntype", . 
        "returns", . 
        "return", . 
        / {"", .
        /
        / filesystem library
        "filesystem library", library. 
        "filesystemlibrary", library. 
        "file library", library. 
        "filelibrary", library. 
        "file lib", library. 
        "filelib", library. 
        "filesystem", library. 
        "filesys", library. 
        "file sys", library. 
        "fs", library. 
        / {"", library.
        / 
        / file creation 
        "file creation", on. 
        "filecreation", on. 
        "create files", on. 
        "createfiles", on. 
        "create a file", on. 
        "createafile", on. 
        "create file", on. 
        "createfile", on. 
        "new file", on. 
        "newfile", on. 
        / {"", on.
        /
        / file deletion 
        "file deletions", on. 
        "filedeletions", on. 
        "file deletion", on. 
        "filedeletion", on. 
        "remove files", on. 
        "removefiles", on. 
        "remove file", on. 
        "removefile", on. 
        "rm file", on. 
        "delete file", on. 
        "delete file", on. 
        "deletefile", on. 
        "delete a file", on. 
        "deleteafile", on. 
        "rm", on. 
        / {"", on. 
        /
        / paths 
        "paths", , 
        "path", , 
        "pat", , 
        / {"", ,
        /
        / directories
        "remove directory", . 
        "removedirectory", . 
        "remove dir", . 
        "removedir", . 
        "directory", . 
        "rmdir", . 
        "dir", . 

        / directory creation
        "createdirectory", reation. 
        "create directory", reation. 
        "createdirectory", reation. 
        "create dir", reation. 
        "createdir", reation. 
        "new directory", reation. 
        "newdirectory", reation. 
        "new dir", reations. 
        "newdir", reation. 
        "mkdir", reation. 
        / {"", .
        /
        / directory iterators 
        "directory iterators", terators. 
        "directoryiterators", terators. 
        "directory iterator", terators. 
        "directoryiterator", terators. 
        "diriterators", terators. 
        "dir iterators", terators. 
        "diriterator", terators. 
        "diriterate", terators. 
        / {"", terators.
        /
        / compilers 
        "compilers", pp"}, 
        "compiler", pp"}, 
        "compile", pp"}, 
        / {"", pp"},
        /
        / gnu gcc
        "gnu compiler", "},
        "gnucompiler", "},
        "gnu compile", "},
        "gnucompile", "},
        "gnu gcc", "},
        "gnugcc", "},
        "gnuc", "},
        "gnu", "},
        "gcc", "},
        / {"", pp"},
        /
        / gnu gcc enable precompiled headers
        "gcc precompile headers", ble_precompiled_headers. 
        "gccprecompileheaders", ble_precompiled_headers. 
        "gcc precompile header", ble_precompiled_headers. 
        "gccprecompileheader", ble_precompiled_headers. 
        "gcc precompile", ble_precompiled_headers. 
        "gccprecompile", ble_precompiled_headers. 
        "precompile headers gcc", ble_precompiled_headers. 
        "precompileheadersgcc", ble_precompiled_headers. 
        "precompile header gcc", ble_precompiled_headers. 
        "precompileheadergcc", ble_precompiled_headers. 
        "precompile gcc", ble_precompiled_headers. 
        "precompilegcc", ble_precompiled_headers. 
        "gcc enable pch", ble_precompiled_headers. 
        "gccenablepch", ble_precompiled_headers. 
        "enable gcc pch", ble_precompiled_headers. 
        "enablegccpch", ble_precompiled_headers. 
        "enable pch gcc", ble_precompiled_headers. 
        "enablepchgcc", ble_precompiled_headers. 
        "gcc pch", ble_precompiled_headers. 
        "pch gcc", ble_precompiled_headers. 
        / {"", ble_precompiled_headers.
        /
        / gnu gcc enable warnings as errors
        "gcc warnings as errors", ble_warnings_as_errors.
        "gcc warnings as error", ble_warnings_as_errors.
        "gccwarningsaserror", ble_warnings_as_errors.
        "gccwarningsaserrors", ble_warnings_as_errors.
        "gccwarningserrors", ble_warnings_as_errors.
        "gcc warnings error", ble_warnings_as_errors.
        "gccwarningserror", ble_warnings_as_errors.
        "gcc warnings", ble_warnings_as_errors.
        "gccwarnings", ble_warnings_as_errors.
        "gccwarning", ble_warnings_as_errors.
        "gcc as errors", ble_warnings_as_errors.
        "gccaserrors", ble_warnings_as_errors.
        "gcc as error", ble_warnings_as_errors.
        "gccaserror", ble_warnings_as_errors.
        "gcc errors", ble_warnings_as_errors.
        "gccerrors", ble_warnings_as_errors.
        / {"", ble_warnings_as_errors.
        /
        / gnu gcc disable extensions 
        "gcc disable extensions", able_extensions.
        "gccdisableextensions", able_extensions.
        "gcc no extensions", able_extensions.
        "gccnoextensions", able_extensions.
        "gcc extensions", able_extensions.
        "gccextensions", able_extensions.
        "gcc remove extensions", able_extensions.
        "gcc remove extension", able_extensions.
        "gccremoveextensions", able_extensions.
        "gccremoveextension", able_extensions.
        "gcc disable ext", able_extensions.
        "gccdisable ext", able_extensions.
        "gcc disabl ext", able_extensions.
        "gccdisablext", able_extensions.
        / {"", h ome + "/code/amples/gnu_gcc_disable_extensions.
        /
        / llvm clang 
        "clang",  
        / {"", 
        /
        / llvm clang enable precompiled headers 
        "clang precompile headers", e_precompiled_headers. 
        "clangprecompileheaders", e_precompiled_headers. 
        "clang precompile header", e_precompiled_headers. 
        "clangprecompileheader", e_precompiled_headers. 
        "clang precompile", e_precompiled_headers. 
        "clangprecompile", e_precompiled_headers. 
        "precompile headers clang", e_precompiled_headers. 
        "precompileheadersclang", e_precompiled_headers. 
        "precompile header clang", e_precompiled_headers. 
        "precompileheaderclang", e_precompiled_headers. 
        "precompile clang", e_precompiled_headers. 
        "precompileclang", e_precompiled_headers. 
        "clang enable pch", e_precompiled_headers. 
        "clangenablepch", e_precompiled_headers. 
        "enable clang pch", e_precompiled_headers. 
        "enableclangpch", e_precompiled_headers. 
        "enable pch clang", e_precompiled_headers. 
        "enablepchclang", e_precompiled_headers. 
        "clang pch", e_precompiled_headers. 
        "pch clang", e_precompiled_headers. 
        / {"", pp"},
        /
        / clang enable warnings as errors
        "clang warnings as errors", e_warnings_as_errors.
        "clang warnings as error", e_warnings_as_errors.
        "clangwarningsaserror", e_warnings_as_errors.
        "clangwarningsaserrors", e_warnings_as_errors.
        "clangwarningserrors", e_warnings_as_errors.
        "clang warnings error", e_warnings_as_errors.
        "clangwarningserror", e_warnings_as_errors.
        "clang warnings", e_warnings_as_errors.
        "clangwarnings", e_warnings_as_errors.
        "clangwarning", e_warnings_as_errors.
        "clang as errors", e_warnings_as_errors.
        "clangaserrors", e_warnings_as_errors.
        "clang as error", e_warnings_as_errors.
        "clangaserror", e_warnings_as_errors.
        "clang errors", e_warnings_as_errors.
        "clangerrors", e_warnings_as_errors.
        / {"", e_warnings_as_errors.
        /
        / clang disable extensions 
        "clang disable extensions", 
        "gccdisableextensions", 
        "clang no extensions", 
        "gccnoextensions", 
        "clang extensions", 
        "gccextensions", 
        "clang remove extensions", 
        "clang remove extension", 
        "gccremoveextensions", 
        "gccremoveextension", 
        "clang disable ext", 
        "gccdisable ext", 
        "clang disabl ext", 
        "gccdisablext", 
        /
        / clang format 
        "clang format",
        "clangformat",
        "formatclang",
        "format clang"
        /
        / clang tidy 
        "clang tidy",  
        "clang_tidy", "clangtidy", "tidy",  
        /
        / msvc  
        / {"microsoft compiler", "microsoftcompiler",  
        /
        / msvc enable precompiled headers 
        "msvc precompile headers",  
        "msvcprecompileheaders",  
        "msvc precompile header",  
        "msvcprecompileheader",  
        "msvc precompile",  
        "msvcprecompile",  
        "precompile headers msvc",  
        "precompileheadersmsvc",  
        "precompile header msvc",  
        "precompileheadermsvc",  
        "precompile msvc",  
        "precompilemsvc",  
        "msvc enable pch",  
        "msvcenablepch",  
        "enable msvc pch",  
        "enablemsvcpch",  
        "enable pch msvc",  
        "enablepchmsvc",  
        "msvc pch",  
        "pch msvc",  
        /
        / msvc enable warnings as errors
        "msvc warnings as errors", 
        "msvc warnings as error", 
        "msvcwarningsaserror", 
        "msvcwarningsaserrors", 
        "msvcwarningserrors", 
        "msvc warnings error", 
        "msvcwarningserror", 
        "msvc warnings", 
        "msvcwarnings", 
        "msvcwarning", 
        "msvc as errors", 
        "msvcaserrors", 
        "msvc as error", 
        "msvcaserror", 
        "msvc errors", 
        "msvcerrors", 
        /
        / msvc disable extensions 
        "msvc disable extensions", 
        "msvcdisableextensions", 
        "msvc no extensions", 
        "msvcnoextensions", 
        "msvc extensions", 
        "msvcextensions", 
        "msvc remove extensions", 
        "msvc remove extension", 
        "msvcremoveextensions", 
        "msvcremoveextension", 
        "msvc disable ext", 
        "msvcdisable ext", 
        "msvc disabl ext", 
        "msvcdisablext", 

        / time complexity
        time,timecomplexity
        /
        / space complexity
        space,spacecomplexity
        /
        / containers
        / containers functions
        /
        / containers iterations
        /
        / containers size functions 
        /
        / access and research functions 
        /
        / static_cast 
        / "static cast",staticcast",
        /
        / maps
        / "map"
        /
        / multimaps
        "multi maps",
        "multimaps", 
        "multimap",
        "multi map", 
        /
        / forward lists singly linked lists
        "forward list",  
        "forwardlist",  
        "forward",  
        "single list",  
        "singlelist",  
        "singly list",  
        "singlylist",  
        "single lists",  
        "singlelists",  
        "singly lists",  
        "singlylists",  
        "singly",  
        /
        / lists functions 
        "lists functions",  
        "listsfunctions",  
        "list functions",  
        "listfunctions",  
        "list function",  
        "listfunction",  
        "listsfunctions",  
        "lists funs",  
        "listsfuns",  
        "lists fun",  
        "listsfun",  
        "list fun",  
        "listfun",  
        / 
        / hash maps 
        "hash maps",
        "hashmaps", 
        "hash map", 
        "hashmap",
        "hashes"
        "hashs",
        "hash",
        /
        / unordered map 
        "unordered maps", 
        "unorderedmaps", 
        "unordered map", 
        "unorderedmap", 
        "unorder maps", 
        "unordermaps", 
        "unorder map", 
        "unordermap", 
        "no order maps", 
        "noordermaps", 
        "no order maps", 
        "noordermaps", 
        "un maps", 
        "unmaps", 
        "un map", 
        "unmap", 
        / 
        / unordered multimap 
        "unordered multimaps", 
        "unorderedmultimaps", 
        "unordered multimap", 
        "unorderedmultimap", 
        "unorder multimaps", 
        "unordermultimaps", 
        "unorder multimap", 
        "unordermultimap", 
        "no order multimaps", 
        "noordermaps", 
        "no order multimap", 
        "noordermultimap", 
        "un multimap", 
        "unmaps", 
        "un map", 
        "unmap", 
        /
        / unordered lists 
        "unordered lists", 
        "unorderedlists", 
        "unordered list", 
        "unorderedlist", 
        "unorder lists", 
        "unorderlists", 
        "unorder list", 
        "unorderlist", 
        "no order lists", 
        "noorderlists", 
        "no order list", 
        "noorderlist", 
        "un lists", 
        "unlists", 
        "un list", 
        "unlist", 
        /
        / unordered sets
        "unordered sets", 
        "unorderedsets", 
        "unordered set", 
        "unorderedset", 
        "unorder sets", 
        "unordersets", 
        "unorder set", 
        "unorderset", 
        "no order sets", 
        "noordersets", 
        "no order set", 
        "noorderset", 
        "un sets", 
        "unsets", 
        "un set", 
        "unset", 
        /
        / unordered multisets
        "unordered multisets", 
        "unorderedmultisets", 
        "unordered multiset", 
        "unorderedmultiset", 
        "unorder multisets", 
        "unordermultisets", 
        "unorder multiset", 
        "unordermultiset", 
        "no order multisets", 
        "noordermultisets", 
        "no order multiset", 
        "noordermultiset", 
        "un multisets", 
        "unmultisets", 
        "un multiset", 
        "unmultiset", 
        /
        / hash functions
        "hashs functions",  
        "hashsfunctions",  
        "hashs function",  
        "hashsfunction",  
        "hashs fun",  
        "hashsfun",  
        "hash functions",  
        "hashfunctions",  
        "hash function",  
        "hashfunction",  
        "hash fun",  
        "hashfun",  
        "hfun",  
        "funh",  
        /
        / queue 
        "a line", , 
        "aline", , 
        "line", , 
        "queues", , 
        "queu", , 
        / {"", ,
        /
        / priority queue 
        "priority queues",  
        "priorityqueues",  
        "priority queue",  
        "priorityqueue",  
        "heaps",  
        "heap",  
        /
        / min heap 
        "min heaps",
        "minheap", 
        "minh", 
        "hmin",
        "heapsmin",
        "heaps min",
        "heap min",
        "heapmin",
        /
        / max heap
        "max heaps"
        "maxheaps",
        "max heap",
        "maxheap", 
        "heapsmax",
        "heapmax", 
        "hmax",
        "maxh",
        /
        / stack
        stack, stacks, stac
        /
        / tries retrieval trees autocomplete 
        "retrieval trees",  
        "retrievaltrees",  
        "retrieval tree",  
        "retrievaltree",  
        "retrieving trees",  
        "retrievingtrees",  
        "retrieving tree",  
        "retrievingtree",  
        "retrieve trees",  
        "retrievetrees",  
        "retrieve tree",  
        "retrievetree",  
        "auto complete",  
        "autocomplete",  
        "autocomp",  
        "tries",  
        "trie",  
        / {"", 
        /
        / trie serialization in json or xml 
        "tries serialization",  
        "tries serializing",  
        "tries serialize",  
        "trie serialization",  
        "trie serializing",  
        "trie serialize",  
        "triesserialization",  
        "triesserializing",  
        "triesserialize",  
        "trieserialization",  
        "trieserializing",  
        "trieserialize",  
        "tries json",  
        "triesjson",  
        "trie json",  
        "triejson",  
        "tries xml",  
        "triesxml",  
        "trie xml",  
        "triexml",  
        "serialization",  
        "serializing",  
        "serialize",  
        / {"", 
        /
        / trees 
        "trees", , 
        "tree", , 
        "tre", , 
        / {"", ,
        /
        / breadth first word_search 
        "breadth first word_search",  
        "breadthfirstsearch",  
        "breadth first",  
        "breadthfirst",  
        "breadth word_search",  
        "breadthsearch",  
        "bread first",  
        "breadfirst",  
        "bread word_search",  
        "breadsearch",  
        "breadthf",  
        "breadths",  
        "breadth",  
        "bread",  
        "bfs",  
        / {"", 
        /
        / depth first word_search 
        "depth first word_search",  
        "depthfirstsearch",  
        "depth first",  
        "depthfirst",  
        "depth word_search",  
        "depthsearch",  
        "dept first",  
        "deptfirst",  
        "dept word_search",  
        "deptsearch",  
        "dep first",  
        "depfirst",  
        "dep word_search",  
        "depsearch",  
        "depthf",  
        "depf",  
        "depths",  
        "depth",  
        "dfs",  
        /
        / graphs 
        "graphes", 
        "graph", 
        "grap", 
        "gra", 
        /
        / sorting algorithms 
        "sorting algorithms",  
        "sortingalgorithms",  
        "sorting algorithm",  
        "sortingalgorithm",  
        "sorting algo",  
        "sortingalgo",  
        "sorting",  
        "sort",  
        / {"", 
        /
        / bubble sort 
        "bubble sorting", . 
        "bubblesorting", . 
        "bubble sort", . 
        "sort bubble", . 
        "sortbubble", . 
        "bubblesort", . 
        "bubble", . 
        / {"", .
        /
        / quick sort 
        "quick sorting",  
        "quicksorting",  
        "quick sort",  
        "sort quick",  
        "sortquick",  
        "quicksort",  
        "quick",  
        "quic",  
        "fast sorting",  
        "fastsorting",  
        "fast sort",  
        "sort fast",  
        "sortfast",  
        "fastsort",  
        "fast",  
        /
        / adjancy lists
        "adjancy lists",  
        "adjancylists",  
        "adjancy list",  
        "adjancylist",  
        "adj lists",  
        "adjlists",  
        "adj list",  
        "adjlist",  
        /
        / adjancy matrix 
        "adjancy matrix",  
        "adjancymatrix",  
        "adj matrix",  
        "adjmatrix",  
        "matrix",  
        "mat",  
        /
        / djiska path 
        "disjka shortest path",  
        "disjkashortestpath",  
        "disjka shortest",  
        "disjkashortest",  
        "disjka short",  
        "disjkashort",  
        "disjka path",  
        "disjkapath",  
        "disjka",  
        "diska shortest path",  
        "diskashortestpath",  
        "diska shortest",  
        "diskashortest",  
        "diska short",  
        "diskashort",  
        "diska path",  
        "diskapath",  
        "diska",  
        "djiska shortest path",  
        "djiskashortestpath",  
        "djiska shortest",  
        "djiskashortest",  
        "djiska short",  
        "djiskashort",  
        "djiska path",  
        "djiskapath",  
        "djiska",  
        "theshortest path",  
        "theshortestpath",  
        "theshortest",  
        "shortest path",  
        "shortestpath",  
        "shortest",  
        "short",  
        /
        / algorithms 
        "algorithms library",
        "algorithmslibrary", 
        "algorithms lib"
        "algorithmslib",
        "algo library", 
        "algolibrary",
        "algo lib", 
        "algolib",
        "al library"
        "allibrary",
        "al lib",
        "allib",
        "algorithms"
        "algorithm",
        "algo", cpp"
        /
        / accumulate
        "accumulates",  
        "accumulat",  
        /
        / puts 
        "algorithm put",  
        "algorithmput",  
        "put algorithm",  
        "putalgorithm",  
        "put algo",  
        "putalgo",  
        "algo put",  
        "algoput",  
        "put std",  
        "std put",  
        "putstd",  
        "stdput",  
        "put",  
        "algorithm puts",  
        "algorithmputs",  
        "puts algorithm",  
        "putsalgorithm",  
        "puts algo",  
        "putsalgo",  
        "algo puts",  
        "algoputs",  
        "puts std",  
        "std puts",  
        "putsstd",  
        "stdputs",  
        "puts",  
        / {"", 
        /
        / cpm cmake package manager
        "cpm package manager",  
        "cpmpackagemanager",  
        "cpm package manage",  
        "cpmpackagemanage",  
        "cpm packager",  
        "cpmpackager",  
        "cpm package",  
        "cpmpackage",  
        "cpm manager",  
        "cpmmanager",  
        "cpm manage",  
        "cpmmanage",  
        "cpm configuration",  
        "cpmconfiguration",  
        "cpm configure",  
        "cpmconfigure",  
        "configure cpm",  
        "configurecpm",  
        "cpm config",  
        "cpmconfig",  
        "cpm conf",  
        "cpmconf",  
        "cpm",  
        / {"",  
        /
        / 
        / conan cmake package manager
        "conan package manager"
        "conanpackagemanager" 
        "conan package manage"
        "conanpackagemanage", h
        "conan packager"
        "conanpackager"
        "conan package"
        "conanpackage", 
        "conan manager",
        "conanmanager", 
        "conan manage", 
        "conanmanage", h
        "conan configuration", 
        "conanconfiguration", h
        "conan configure", home
        "conanconfigure", home 
        "configure conan", home
        "configureconan", home 
        "conan config", home + 
        "conanconfig", home + "
        "conan conf", home + "/
        "conanconf", home + "/c
        "conan", home + "/code/
        // {"", home + "/code/cp
